---
title: "Moon_Logbook_KO"
author: "Sang Hyo Moon"
date: "2024-02-03"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
    code_folding: "hide"
    
editor_options: 
  markdown: 
    wrap: 72
---

don't run a code but show it eval = FALSE


```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = TRUE, # show all code
    tidy = FALSE, # cleaner code printing
    size = "small", # smaller code
    
    fig.path = "figures/", #graphics location
    out.width = "100%",

    message = FALSE,
    warning = FALSE,
    cache=TRUE,
    results = "hide",
    message = FALSE,
    warning = FALSE
    
    
    )
```

```{r, include=FALSE}
    require(chillR)
    require(ggplot2)
    require(reshape2)
    require(kableExtra)

```

weather station in Korea <https://minwon.kma.go.kr/main/obvStn.do>

CHEONGJU 36.63924 127.44066 58.7 Apfel hof 30km weiter weg von der
Wetter stastion

```{r}
# download weather station list for the vicinity of Bonn
Cheong_station_list <- handle_gsod(action = "list_stations",
                            location=c(127.44066,  36.63924))
```

Yangpyeong 37.48863 127.49446 47.26 Paju 37.88589 126.76648

Suwon 37.25746 126.983 39.81

Gwangju 35.17294 126.89156 70.28

Busan 35.10468 129.03203 69.56

wando 34.3959 126.70182

gunsan 36.0053 126.76135

gimhae 35.22981 128.89075

KAESONG KN 37.967 126.567 19570202 20231111 19.71 63.91

대관령 37.67713 128.71834

37.48129 130.89864

sri lanka 7 81

```{r}
# download weather station list for the vicinity of Bonn
Yang_station_list <- handle_gsod(action = "list_stations",
                            location=c(81,  7))
```

# Korean data

-   apple production:
    <http://www.nongsaro.go.kr/portal/ps/psb/psbx/cropEbookFileViewPop.ps?indexPage=9&indexBasePage=0&cropsEbookFileNo=00001&ebookCode=8>
-   pear production:
    <http://www.nongsaro.go.kr/portal/ps/psb/psbx/cropEbookFileViewPop.ps?indexPage=9&indexBasePage=3&cropsEbookFileNo=00002&ebookCode=13>

CHUPUNGNYEONG: 36.22025 127.99458 244.98 산사과 농장: 경북 영동군
추풍령면 학동길 83 산사과농장 (contact) around 700m away from weather
station no data...

```{r}
# download weather station list for the vicinity of Bonn
KO_station_list <- handle_gsod(action = "list_stations",
                            location=c(127.99458,  36.22025))

	
CHUPUNGNYEONG_weather <- handle_gsod(action = "download_weather",
                            location = KO_station_list$chillR_code[1],
                            time_interval = c(1973,2019)) %>%
  handle_gsod()
```

Daegu 35.87797 128.65295 54.27

```{r}
# download weather station list for the vicinity of Bonn
Daegu_station_list <- handle_gsod(action = "list_stations",
                            location=c(128.65295,  35.87797))
```

Naju

GWANGJU 35.126 126.809 19531201 20230829 67.09 (Gwangju airport) to Naju
(city of pears) around 20km away

lack of data... there is no farms where wrote the blooming date asked to
pear institute in Korean agricultural chamber and to pear center in
agricultural technique center in Naju

interview: expert of forestry: no data in Korea. recommended korean
samrt farm sector (around 6 years) old)

나주는

# Introduction

# tools

# tree dormancy
